\chapter{Software Requirements Specification}
\label{appendix:srs}

\section{Introduction}
\subsection{Purpose}
\label{appendix:srs:purpose}

The purpose of this Requirements Specification is to document the software requirements of Fale Alguma Coisa, a citizen science voice recording app. It should be used by anyone with the intent of understanding what are the capabilities of the system. This document will not focus on how the system will be built, but serves as the basis for the design and implementation. The design is documented within the Design Model in appendix \ref{appendix:design-model}. Details on implementation are documented in the corresponding Software Design Description (SDD) document in the appendix \ref{appendix:software-design-description}.

\subsection{Scope}
\label{appendix:srs:scope}

\subsubsection{Objectives}

Towards contributing \textbf{nonprofessional scientists}, the Fale Alguma Coisa app should provide an easy gateway for the user to contribute his voice while having fun and learning various science facts and curiosities.

Towards researching \textbf{scientists}, the Fale Alguma Coisa app should provide a database of anonymized voice recordings, for scientists to extract and create speech corpus.

\subsubsection{Outside scope}

However, some elements are outside of the scope of this system. Fale Alguma Coisa should \textbf{not}:
\begin{itemize}
    \item Allow for association of recording data and personal identification data (name, email);
    \item Support internationalization in the WebApp;
    \item Convert audio data into another format
    \item Support offline recording
\end{itemize}

\subsubsection{Artefacts}
\label{appendix:srs:artefacts}

This document identifies the following artifacts to be produced:

\begin{itemize}
    \item Context
    \item Domain Model
    \item Use Case Requirements (Actors, Diagrams, Specifications)
    \item Activity Diagrams
    \item Non-Functional Requirements
    \item Interface Requirements
    \item WebApp for user recordings
    \item Backend integrating with database
    \item Database structure
\end{itemize}

\subsection{Overview of Document}

This overview provides a summary of the contents of each section of this document.

\begin{itemize}
    \item Introduction
    \item System Overview
    \item Domain Model
    \item Requirements
\end{itemize}

\subsection{References}

\begin{itemize}
    \item Based on: \cite{naoufel2014requirements}
    \item Supporting literature: \cite{pressman2014software}
\end{itemize}

\section{System Overview}
\label{appendix:srs:system-overview}

The System Overview section presents the system context and design, and also discusses the background of the Fale Alguma Coisa project.

\subsection{Name}

This system is called "Fale Alguma Coisa". This is a phrase in brazillian portuguese to order someone to "say something". It is also common to hear "fala alguma coisa", but this was changed to remove the alliteration effect, providing easier spelling.

\subsection{System Context}

This system is originated from the need of recording anonymized user voices throughout the use of gamification and citizen science.

\subsection{General Constraints}

This system is mainly impacted by constraints in data privacy. Recordings should never be associated with the users personal data (such as email), but should have metadata to aid in corpus construction, such as age interval, gender, and dialect.

\subsection{Assumptions and Dependencies}

The system heavily depends on the phrases that will be spoken. Therefore, it is necessary to provide this application with a comprehensive list of phrases before the application general publication.

\section{Requirements}
\label{appendix:srs:requirements}

To accurately describe the software requirements of a project, it is important to understand the requirements from many different perspectives. The analysis model proposed by \cite{pressman2014software} encompasses four different modeling elements (perspectives) that can be used to provide the most effective bridge to software design. They are listed in the subsections below as (1) scenario based models, (2) class-based elements model, (3) behavioral elements, and (4) flow-oriented elements. The analysis can lead to the derivation of one or more of these modeling elements, since one model may not completely describe certain functionalities of the app. Additionally, the actor list will be provided in the table \ref{tab:actor-list} below:

\begin{table}[h]
\centering
\caption{WebApp Fale Alguma Coisa Actor List}
\label{tab:actor-list}
\begin{tabular}{|p{2.5cm}|p{3.5cm}|p{7cm}|}
    \hline 
    Actor & Responsibilities & Description  \\ \hline
    Unregistered Citizen & Record phrases & User that has not logged on in the WebApp, and has not added his metadata \\ \hline
    Registered Citizen & Record phrases with metadata & User that has added his metadata on the WebApp \\ \hline 
    Validation Scientist & Validate recorded phrases & Download and validate recordings \\ \hline
    Corpus User & Download validated phrases & Access the open speech corpus and download it \\ \hline
\end{tabular}
\caption*{Source: Author}
\end{table}

\subsection{Scenario-based models}
\label{appendix:srs:scenario-based-models}

This model depicts how the user interacts with the system and the specific sequence of activities that occur as the software is used. One common implementation for this specification is through use cases. To provide scenario-model completeness, the following sections will describe every use case mapped to the WebApp. They are, however, not extensive to the functionality of the application, some use cases are complemented by the models cited above. Each of the use cases are categorized by feature. Furthermore, each feature is described in the table \ref{tab:falealgumacoisa-features}.

\begin{table}[h]
    \centering
    \caption{WebApp Fale Alguma Coisa Features}
    \label{tab:falealgumacoisa-features}
    \begin{tabular}{|p{3cm}|p{10cm}|}
        \hline Epic & Description \\
        \hline Home & Represents the use cases affecting the homepage, such as the splash screen, call to action button, terms of service, etc. \\
        \hline Recording & Represents the most important feature in the application, as the citizen will use it to record his voice. It also provides supporting features, such as skipping phrases and resuming the recording session.\\ 
        \hline Dashboard & Lists all user stories related to the dashboard page, such as where the user will be able to choose themes to record, open the menu, check his level, etc. \\
        \hline Gamification & Details the engagement component of the application. Elements such as leaderboards, points and levels are described. They add a sense of progress to the user experience. \\
        \hline Social & To allow social interaction with other users, this feature lists social features to be added to the application. \\
        \hline Login and Registration & The application should provide user authentication to enable data management and progress saving. \\
        \hline
    \end{tabular}
    \caption*{Source: Author}
\end{table}

\input{use-cases}

\clearpage
\subsection{Class models}
\label{appendix:srs:domain-model}

Understanding the domain of the proposed application will assist in creating a better data structure. Below are some examples using class diagrams of the most common objects used by the system, such as recordings and phrases.

\subsection{User Recording}

Represents the all data generated by the user, containing the following elements below:

\begin{itemize}
    \item metadata, if the user registered it
    \item notifications, if the user has received any
    \item themes, if the user has at least recorded one phrase (just groups the phrases)
    \item phrase, if the user has at least recorded one phrase
\end{itemize}

\begin{figure}
    \caption{Class diagram for the UserRecording}
    \label{fig:userrecording-class-diagram}
    \begin{center}
    \begin{tikzpicture}
    \begin{umlpackage}{User}
    \umlclass[y=-10]{UserRecording}{}{}
    \umlclass[x=5, y=-5]{UserData}{
        firebaseId : string \\
        nickname : string \\
        gender : string \\
        ageInterval : string \\
        region : string \\
        dialect : string \\
        referralCode : string
    }{}
    \umlclass[x=5,y=-10]{UserNotification}{
        type : string \\
        dismissed : boolean \\
        scoringId : string \\
        name : string
    }{}
    \umlclass[x=5,y=-15]{RecordingTheme}{
        title : string \\
        finished : boolean \\
        recordings : RecordingPhrase[]
    }{}
    \umlclass[x=12,y=-15]{RecordingPhrase}{
        phraseId : string \\
        sampleRate : int \\
        format : string \\
        duration : string \\
        recordingPath : string \\
        skippedReason : string
    }{}
    
    \umlassoc[geometry=|-, mult=1, pos=1.9]{UserRecording}{UserData}
    \umlassoc[geometry=-|, mult=*, pos=0.3]{UserRecording}{UserNotification}
    \umlassoc[geometry=|-, mult=*, pos=1.9]{UserRecording}{RecordingTheme}
    \umlassoc[geometry=|-, mult=*, pos=1.9]{RecordingTheme}{RecordingPhrase}
    \end{umlpackage}
    \end{tikzpicture}
    \end{center}
    \caption*{Source: Author}
\end{figure}

\subsection{Behavioral models}
\label{appendix:srs:behavioral-models}

The inclusion of behavioral models is not deemed necessary to this specification.

\subsection{Flow models}
\label{appendix:srs:flow-models}

The inclusion of flow models is not deemed necessary to this specification.

\section{Design Model}
\label{appendix:srs:design-models}

\section{User Interface Design}
\label{appendix:user-interface-design}

All user interfaces designed are available in the Zeplin interface. Refer to the link \url{https://zpl.io/a3WMkjW} for the complete list.

\section{Nonfunctional Requirements}
\label{appendix:srs:nonfunctional-requirements}

The nonfunctional requirements for a system are typically constraints on the functional requirements – that is, not what the system does, but how it does it (e.g. how quickly, how efficiently, how easily a task is achieved from the user’s perspective, etc.).

Other nonfunctional requirements may be required characteristics that are not part of the system’s functionality, e.g., conformance with legal requirements, scalability, interoperability, etc. They are specified below.

\subsection{System Requirements}

A web application will be developed. If possible, compatible with all modern browsers (Chrome, Firefox, Safari, Edge), in mobile and desktop versions.

\subsection{Usability Requirements}

This system is aimed towards nonprofessionals, so there should be little to no technical jargon present.

\subsection{Performance Requirements}

There are no performance requirements.

\subsection{Security Requirements}

For the WebApp, the logged area must be protected by an authorization layer. The other areas, such as homepage, terms of service and recording page are not necessarily protected.

All the functionality of the backend must be protected from public access. If necessary, the user must provide an anonymous token to vouch for authenticity.

The database must not be accessible from the public, only by the backend or local access.

\subsection{Delivery Requirements}

The application should be delivered to a local USP server, since it will host all applications and data.

\subsection{Legal Requirements}

This research relies on the fact that if consent is given by the user, user data can be collected and utilized for scientific purposes. This is one of the articles of the LGPD law.

\subsection{Interoperability Requirements}

To provide authentication, this system will interact with the authorization provider, Firebase. For logging purposes, Sentry is integrated with the WebApp and the Backend.

\subsection{Scalability Requirements}

The Fale Alguma Coisa has no specific scalability requirements.